S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
comment on kernel isotropy in discussion

% TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}

 % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
 \documentclass[10pt]{article}

@@

The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions. This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

>>>>

% TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
 % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
 \documentclass[10pt]{article}

@@

The fact that the connectivity kernel is isotropic about the origin \parham{it's true for isotropic kernel in general not only about origin} means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions. This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
